\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{Traducción}

\begin{document}

\section*{\centering{English Text}}

When I am in a bad mood, I clean the house. I clean every room and I wash the clothing. I work for many hours because our house is big. Some people work when they are in a bad mood, and others read a book or eat a lot of food. I live with three people and a cat. Sometimes we are happy and sometimes we are sad. In other words, we are normal. We are from India, but now we live in Sri Lanka. Our house is near the coast. Sri Lanka is an island in the Indian Ocean. Sri Lanka exports a lot of tea and coffee. When my mother prepares coffee or tea, it is delicious. My father is a doctor and my mother is an artist. They are kind. My sister is very tall. Our cat is black and gray. Where are you from? Where are you now?

\section*{\centering{Translation}}

Cuando estoy de mal humor, limpio la casa. Limpio cado cuarto y lavo la ropa. Trabaja muchas horas porque nuestra casa es muy grande. Algunas personas trabajan cuando estan de mal humor, y otras leen un libro o comen mucha comida. Vivo con tres personas y una gata. A veces estamos felices y a veces estamos tristes. In otras palabras, somos normales. Somos de la India, pero ahora viven en Sri Lanka. Nuestra casa es cerca de la costa. Sri Lanka es una isla en el Océano Indico. Sri Lanka exporta muchos té y café. Cuando mi madre prepara café o té, es delicioso. Mi padre es médico y mi madre es artista. Son amables. Mi hermosa es muy alta. Nuestra gata es negra y gris. ¿De dónde eres? ¿Dónde estás ahora?

\end{document}
